Autoreduction - an automated data reduction system for beam instruments

### 2016-09-21 Documentation/paper/paper.tex
Added some screenshots and citations.

\documentclass[twocolumn]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\date{}

\begin{document}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Automate the reduction of data from beam instruments, using scripts
  provided by instrument scientists.
\item
  Show the status of reduction on runs, as well as the results and
  locations of reduced data, to users.
\item
  Allow instrument scientists to set the parameters used for reduction,
  in advance and retroactively.
\item
  Allow users and instrument scientists to see what script, with which
  parameters, was used to reduce a run.
\item
  Allow users and instrument scientists to modify the parameters used
  for a run, and re-run reduction using new parameters or scripts.
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Limit access to the system to ensure that only staff and scientists
  can access runs and instruments.
\item
  Utilise existing authentication systems to validate identities and
  permissions for (1).
\item
  Allow scalability for processing large amounts of data in a timely
  manner.
\item
  Integrate with ICAT -- the scientific metadata catalogue in use at
  ISIS.
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  A listener for new jobs
\item
  The state database \& coordinator
\item
  Workers for reduction processing
\end{enumerate}

@@

@@

Apache ActiveMQ is used as the message queueing system, with message
contents as JSON-formatted objects. The intention of the message is
conveyed by which queue it's placed in, rather than a field in the
message itself. Runs can be `scheduled' simply by using ActiveMQ's
scheduled delay feature, which allows a message to be delivered a given
time after it's been pushed to the queue.

@@

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Expanding the system to accommodate greater volume of use -- this
  might involve adding more reduction workers, for example.
\item
  Integrating other methods of listening for new runs -- the current
  method of watching a file archive is specific to ISIS.
\item
  Improving portability and deployability of the current software; the
  state database/webapp in particular is currently unsupported for
  Linux, and the whole system is somewhat nontrivial to deploy even to a
  development environment.
\end{enumerate}

\end{document}

>>>>

\documentclass[twocolumn]{article}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Autoreduction - an automated data reduction system for beam instruments},
            pdfauthor={J. R. Corderoy - ISIS Facility, Rutherford Appleton Laboratory - jrc91@cam.ac.uk},
            pdfborder={0 0 0},
            breaklinks=true}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

\title{Autoreduction - an automated data reduction system for beam instruments}
\author{J. R. Corderoy - ISIS Facility, Rutherford Appleton Laboratory -
jrc91@cam.ac.uk}
\date{23/09/2015}

\begin{document}
\maketitle

\subsection*{Abstract}\label{abstract}

\section{Introduction}\label{introduction}

@@

\begin{enumerate}
\item
  Automate the reduction of data from beam instruments, using scripts
  provided by instrument scientists.
\item
  Show the status of reduction on runs, as well as the results and
  locations of reduced data, to users.
\item
  Allow instrument scientists to set the parameters used for reduction,
  in advance and retroactively.
\item
  Allow users and instrument scientists to see what script, with which
  parameters, was used to reduce a run.
\item
  Allow users and instrument scientists to modify the parameters used
  for a run, and re-run reduction using new parameters or scripts.
\end{enumerate}

@@

\begin{enumerate}
\item
  Limit access to the system to ensure that only staff and scientists
  can access runs and instruments.
\item
  Utilise existing authentication systems to validate identities and
  permissions for (1).
\item
  Allow scalability for processing large amounts of data in a timely
  manner.
\item
  Integrate with ICAT \cite{icat} -- the scientific metadata catalogue in use
  at ISIS .
\end{enumerate}

@@

\begin{enumerate}
\item
  A listener for new jobs
\item
  The state database \& coordinator
\item
  Workers for reduction processing
\end{enumerate}

@@

\begin{figure*}[!htbp]
\includegraphics{system.png}
\caption{How the autoreduction system fits into the ISIS workflow.}
\end{figure*}

@@

Apache ActiveMQ \cite{activemq} is used as the message queueing system, with
message contents as JSON-formatted objects. The intention of the message
is conveyed by which queue it's placed in, rather than a field in the
message itself. Runs can be `scheduled' simply by using ActiveMQ's
scheduled delay feature, which allows a message to be delivered a given
time after it's been pushed to the queue.

@@

\begin{figure*}
\centering\includegraphics[width=0.8\linewidth]{index.png}
\caption{The web app index, showing recent runs.}
\end{figure*}

@@

\begin{enumerate}
\item
  Expanding the system to accommodate greater volume of use -- this
  might involve adding more reduction workers, for example.
\item
  Integrating other methods of listening for new runs -- the current
  method of watching a file archive is specific to ISIS.
\item
  Improving portability and deployability of the current software; the
  state database/webapp in particular is currently unsupported for
  Linux, and the whole system is somewhat nontrivial to deploy even to a
  development environment.
\end{enumerate}

\section{Conclusion}\label{conclusion}

\begin{thebibliography}{9}
\bibitem{icat}
    The ICAT Collaboration,
    \emph{The Icat Project.},
    2014,
    \href{https://doi.org/10.5286/SOFTWARE/ICAT}{10.5286/SOFTWARE/ICAT}.

\bibitem{activemq}
    Apache Software Foundation,
    \emph{Apache Activemq},
    \url{http://http://activemq.apache.org/},
\end{thebibliography}
\end{document}
